Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-03 bbbq_article.tex
Show conservation scores from bbbq_2, show IC50 values for binders per haplotype from the 'ic50s_per_haplotype' folder

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1/fig_ic50_distribution.png}
  \caption{
    Distribution of IC50 estimations per haplotype per target.
    The IC50 value is plotted on a logarithmic scale.
  }
  \label{fig:1}
\end{figure}

@@

In this study, a peptide is defined a binder (for a haplotype), 
if \emp{within a proteome} in which it is found, 
is within the peptides with the 2\% lowest IC50 values.

\input{bbbq_1/table_ic50_binders.latex}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{IC50s per haplotype}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{COVID-19 TMHs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{tmhs/tmhs.png}
  \caption{
    Location of amino acids of reference COVID-19 
    proteome (Uniprot ID: UP000464024).
    Note that ORF1a results in multiple proteins, 
    as shown in figure \ref{fig:covid_genome_and_proteome}.
    Legend: 1 = located in the membrane, 0 = not located in the membrane.
    Topology obtained using 'pureseqtmr' \cite{pureseqtmr}
  }
  \label{fig:covid_topology}
\end{figure}

\begin{table}[!htbp]
  \input{tmhs/covid_tmhs.latex}
  \caption{
    Number of TMHs per COVID-19 ORF,
    using 'pureseqtmr' \cite{pureseqtmr}
  }
  \label{table:covid_tmhs}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evolutionary conservation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_boxplot.png}
  \caption{
    Evolutionary conservation
  }
  \label{fig:evolutionary_conservation_boxplot}
\end{figure}

@@

@@

In this study, a peptide is defined a binder (for a haplotype), 
if \emp{within a proteome} in which it is found, 
is within the peptides with the 2\% lowest IC50 values.
Subsection \ref{subsec:ic50s_per_haplotype} shows the IC50 values
for a binder per haplotype.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evolutionary conservation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores.png}
  \caption{
    Evolutionary conservation
  }
  \label{fig:evolutionary_conservation_tmh}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_all.png}
  \caption{
    Evolutionary conservation
  }
  \label{fig:evolutionary_conservation_all}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{IC50s per haplotype}
\label{subsec:ic50s_per_haplotype}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@
